Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-02-07 tex/sections/apm.tex
Clarify section 3.2
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Assume that we have a component which has a considerable arithmetic circuit complexity. If this complex component
is needed in some arbitrary computation steps, we will need to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround. Instead of
repeating the circuit of the component, we can use a simpler cryptographic hash calculator circuit during the
computation, and use a final verification circuit at the end to verify the functionality of the component.

Every component accepts an input $in$ and produces an output $out$. As a result we can denote the component by a
deterministic function that maps an input sequence with any arbitrary length $k$, to an output sequence with the same
length:
\[
    f((in_1,in_2,\dots,in_k)) \coloneqq (out_1,out_2,\dots,out_k)
\]
In every step of the computation, we replace this component with a cryptographic hash calculator which receives $in$ and
$out$ as its inputs and gets activated in the same computation steps that the component must be active. When the
hash calculator is active, it hashes its inputs, so at the end of the computation it has computed a digest:
\[
    h(in_1,out_1,in_2,out_2,\dots,in_k,out_k) \coloneqq digest_f
\]
where $k$ is the number of steps that our component must have been active.

@@

Interestingly, this approach can also reduce the number of computation steps. When we use a hash calculator circuit
instead of our component, $out$ will be available in the same computation step that $in$ is available. This will
eliminate the computation step that is needed for generating $out$ by the component's circuit.
%
%\begin{tikzpicture}
%    \draw (0,0) -- (4,0) -- (4,4) -- (0,4) -- (0,0);
%\end{tikzpicture}

>>>>

Assume that we have a computing machine $M$, that accepts an input $in$ and produces an output $out$. We want to
calculate the output that results from applying $M$ on an initial input for $n$ times. Note that
$M$ may not be state-less:
\[
    M_n(in_1, out_1, out_2,\dots,out_{n-1}) \coloneqq out_n
\]

We assume that $M$ is composed of a number of subcomponents. Every subcomponent is like a computing machine and accepts
an input and produces an output. Like $M$, subcomponents are not necessarily state-less. When $M$ receives an input,
based on the input, a number of subcomponents gets activated, they generate their output from the input, and then
their outputs are combined to produce the output of $M$.

To build a verifying circuit for this computation, we need to construct a circuit for $M$ and then repeat this circuit
$n$ times to compute $out_n$ at the final step of the computation.\footnote{Since $M$ is not state-less, we may have
to feed inputs from steps, say, $i-1,i-2,\dots$ to step $i$.}

Assume that we have a subcomponent that has a considerable arithmetic circuit complexity. Even if this subcomponent is
active in only a few computation steps, We will still have to repeat its circuit in every step of the computation. This
will increase the complexity of proof generation considerably. Fortunately, there is a workaround. Instead of
repeating the circuit of the component, we can use a simpler cryptographic hash calculator circuit during the
computation. At the end, to verify the functionality of the component, we use a final verification circuit.

Every subcomponent accepts an input $in$ and produces an output $out$. If the component gets activated for $k$ steps, we
can denote it by a deterministic function that maps an input sequence with length $k$, to an output sequence with the
same length:\footnote{Note that subcomponents are not active in every step of the computation, so $in_i$ is \textbf{not}
indicating the input of the component at the $i$th step of the computation.}
\[
    f((in_1,in_2,\dots,in_k)) \coloneqq (out_1,out_2,\dots,out_k)
\]
In every step of the computation, we replace this component with a cryptographic hash calculator which receives $in$ and
$out$ as its inputs and gets activated in the same computation steps that the component must be active. When the
hash calculator is active, it hashes its inputs, so at the end of the computation it has computed a digest:
\[
    h(in_1,out_1,in_2,out_2,\dots,in_k,out_k) \coloneqq digest_f
\]
where $k$ is the number of steps that our component must have been active.

@@

Interestingly, this approach can also reduce the number of computation steps. When we use a hash calculator circuit
instead of our component, $out$ will be available in the same computation step that $in$ is available. This will
eliminate one computation step that is needed for generating $out$ by the component's circuit.
%
%\begin{tikzpicture}
%    \draw (0,0) -- (4,0) -- (4,4) -- (0,4) -- (0,0);
%\end{tikzpicture}
